Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-25 document/ms.tex
title
intro text tweaks

\title{%
    Inferring the rate of Earth-like exoplanets from noisy data
}

@@

When we make conclusions about the radius disribution of exoplanets,
  the distribution parameters are not nuisances but in fact our object.
Even then, however, our results will have the period parameters marginalized out.

Perhaps the most important novelty of this study is in its treatment of errors.
Although planet periods are usually precisely measured,
  planet radius measurements near Earth radius have large uncertainties.
The justified probabilistic approach to including these uncertainties in a distribution analysis
  is to introduce the ``true'' radii as latent variables and infer and marginalize them out
  along with all other nuisance parameters.
Although this sounds expensive---and it can be---%
  there is a simple approach we have been advocating (CITE HOGG) that makes use of importance sampling.
We use this approach here;
  our results are fully marginalized over posterior uncertainties in all of the planet radii.
More will be said about this below;
  the importance sampling looks like a product over data points
  of sums (averages) over individual-datum radius samplings.

>>>>

\title{%
  Inferring the distribution and rate of Earth-like exoplanets \\
  from noisy individual-planet inferences
}

@@

When, in what follows, we ask questions about the radius disribution of exoplanets,
  the distribution parameters are no longer nuisances
The radius-distribution parameters are what we are trying to measure.
Even in this case, however, our results will have the period-distribution parameters marginalized out.

Perhaps the most important novelty of this study is in its treatment of observational uncertainties.
Although planet periods in our data set are very precisely measured,
  the planet radius measurements have large uncertainties.
The justified probabilistic approach to including these uncertainties in a distribution analysis
  is to introduce the ``true'' radii as latent variables and infer and marginalize them out
  along with all other nuisance parameters.
Although this sounds expensive---and it can be---%
  there is a simple approach we have been advocating (CITE HOGG) that makes use of importance sampling.
We use this approach here;
  our results are fully marginalized over posterior uncertainties in all of the planet radii.
More will be said about this below;
  the importance sampling looks like a product over data points
  of sums (averages) over individual-datum radius samplings.
